RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-05 assets/simulation/region_comparison.tex
:bento: Update assets

\begin{axis}[%
width=4.079in,
height=1.587in,
at={(0.684in,0.361in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter\\Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
align=center,
title style={font=\LARGE},
label style={font=\LARGE},
ticklabel style={font=\Large},
legend style={font=\Large},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

>>>>

\begin{axis}[%
width=4.014in,
height=1.552in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter\\Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
title style={font=\LARGE},
label style={font=\LARGE},
ticklabel style={font=\Large},
legend style={font=\Large},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}
